---
title: "A Script for analyzing the second Pilot's data"
author: "Aziz Abubshait"
date: "4/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## R Markdown

```{r read-in data, echo = F}
pilot_path = paste(getwd(), "/pilot2_data_raw/", sep = "")
list_of_datanames = list.files(pilot_path)
dat_p2 = lapply(paste(pilot_path, list_of_datanames, sep = ""), read.csv)
dat_p2 = do.call(plyr::rbind.fill, dat_p2)
```

```{r, ## We will manually code the subjective data, echo = F}
data_quest = data.frame(
  participant = c("1_2", "3_4", "5_6", "7_8", "9_10", "11_12", "13_14",
                  "15_16"),
             #1  3  5  7  9 11  13 15
  p1_resp = c(6, 2, 5, 3, 4, 4, 5, 3), 
             #2  4  6  8 10 12  14 16
  p2_resp = c(1, 2, 3, 2, 4, 5, 2, 4))
```

```{r now do some data preprocessing, echo = F}
# ind = seq(1, nrow(dat_p2), by=11)
# dat_p3 = dat_p2[ind, ]

dat_clean = dat_p2 %>% 
  group_by(participant) %>% 
  # get rid of practice trials
  slice(-c(1:2)) %>% 
  # we need to recode to 1 and 2 because the fill function won't work for characters. 
  # It only works for numeric variables
  mutate(
    RespTuringLeft = 
           case_when(RespTuringLeft == "c" ~ 1,
                     RespTuringLeft == "h" ~ 2),
    RespTuringRight = 
           case_when(RespTuringRight == "c" ~ 1,
                     RespTuringRight == "h" ~ 2)) %>% 
  fill(RespTuringLeft, .direction = "up") %>%
  fill(RespTuringRight, .direction = "up") %>%
  fill(keyTuringLeft.corr, .direction = "up") %>%
  fill(keyTuringRight.corr, .direction = "up") %>%
  mutate(
    RespTuringLeft = recode(
      RespTuringLeft, `1` = "comp", `2` = "human")) %>%
  mutate(
    RespTuringRight = recode(
      RespTuringRight, `1` = "comp", `2` = "human")) %>%
  # remove some vars
  select(-c(1:4,7:12, 15:17, 19:70)) %>%
  ## Delete every 11th row
  filter(
    is.na(Number)==F,
    is.na(key_respLeft.rt) == F,
    is.na(key_respRight.rt) == F
    ) %>%
  left_join(data_quest, by = "participant") %>% 
  mutate(
    # measure synchrony
    sync_value = abs((key_respLeft.rt-key_respRight.rt))/
      (key_respLeft.rt+key_respRight.rt)*100,
    choice = case_when(RespTuringRight == "comp" &
                         RespTuringLeft == "comp" ~ 
                         "comp_congruent",
                            RespTuringRight == "comp" & 
                              RespTuringLeft == "human" ~ 
                         "incongruent",
                            RespTuringRight == "human" & 
                              RespTuringLeft == "comp" ~ 
                         "incongruent",
                            RespTuringRight == "human" & 
                              RespTuringLeft == "human" ~
                         "human_congruent"),
         closeness_diff = abs(p1_resp - p2_resp),
         closeness_avg = mean(c(p1_resp, p2_resp))) %>% 
  mutate(sync_z_value = scale(sync_value)) %>% 
  ungroup(participant)
```

## Here are some Plots to visualize the results

## First, is how many instances of choices do we have?
```{r, fig.height=8, fig.width=8}
dat_clean %>%
  group_by(participant, Partner, Block.thisN) %>% 
  summarize(choice = first(choice)) %>%
  ggplot(aes(x = Partner, fill = choice))+
    geom_histogram(stat="count", position = position_dodge(.9), 
                   color = "black",
                   lwd = 1, alpha = .8)+theme_bw()+
  geom_text(stat='count', aes(label=round(..count..)), 
            position = position_dodge(.9), vjust=2) +
  labs(title = "number of choices for all participants")

dat_clean %>%
  group_by(participant, Partner, Block.thisN) %>% 
  summarize(choice = first(choice)) %>%
  ggplot(aes(x = Partner, fill = choice))+
    geom_histogram(stat="count", position = position_dodge(.9), 
                   color = "black",
                   lwd = 1, alpha = .8)+theme_bw()+
  geom_text(stat='count', aes(label=round(..count..)), 
            position = position_dodge(.9), vjust=2) +
  facet_wrap(~participant)+
  labs(title = "number of choices for for each dyad")
  
```

## Next, we have the actual sync values. Sync values are calculated as percentages.
## RT_participant1 - RT_participant2 / (RT_participant1 + RT_participant2)
```{r}
dat_clean %>%
  ggplot(aes(y = sync_value, x = Partner, color = choice))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.3),
               fun.args = list(mult = 1))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.3))+
  theme_bw()+
  labs("Sync valye for each agent by participant choice")

dat_clean %>%
  ggplot(aes(y = sync_value, x = Partner))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.3),
               fun.args = list(mult = 1))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.3))+
  theme_bw()+
  labs("Sync valye for each actual partner")

dat_clean %>%
  ggplot(aes(y = sync_value, x = Partner, color = choice))+
  geom_point(shape = 1, alpha = .8, position = position_jitterdodge(.1))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.8),
               fun.args = list(mult = 1.96))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.8))+
  theme_bw()+
  labs("Sync valye for each agent by participant choice with individual data points")
```
## What about the correlations between sync values and subjective ratings of closeness?
```{r Correlations}
dat_clean %>% ggplot(aes(x = closeness_diff)) + geom_histogram()+
  labs(title = "we have a good spread of subjective data")
dat_clean %>% ggplot(aes(x = closeness_avg)) + geom_histogram()+
  labs(title = "we have a good spread of subjective data here too")

dat_clean %>%
  ggplot(aes(sync_value, closeness_diff, color = Partner))+
  geom_point()+
  geom_smooth(method = "lm", se =F)

dat_clean %>%
  ggplot(aes(sync_value, closeness_avg, color = Partner))+
  geom_point()+
  geom_smooth(method = "lm", se =F)

```

## Now lets look at the same data but exclude sync values beyond 6 SD.
```{r data without the points beyond 6 SD, echo = F}
## Now do some preprocessing
dat_clean2 = dat_clean %>% 
  filter(sync_z_value < 6)
```

```{r}
dat_clean2 %>%
  ggplot(aes(y = sync_value, x = Partner, color = choice))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.3),
               fun.args = list(mult = 1))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.3))+
  theme_bw()+
  labs(title = "Sync value for each agent by participant choice within 6 SD")

dat_clean2 %>%
  ggplot(aes(y = sync_value, x = Partner))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.3),
               fun.args = list(mult = 1))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.3))+
  theme_bw()+
  labs(title = "Sync valye for each actual partner within 6 SD")

dat_clean2 %>%
  ggplot(aes(y = sync_value, x = Partner, color = choice))+
  geom_point(shape = 1, alpha = .8, position = position_jitterdodge(.1))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.8),
               fun.args = list(mult = 1.96))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.8))+
  theme_bw()+
  labs(title = "Sync valye for each agent by participant choice with individual data points within 6 SD")

```

## Participants 11 and 12 were cheating. So we will remove them as well. 
```{r data without dyad 11/12, echo = F}
dat_clean2 %>% 
  filter(!participant %in% c("11_12")) %>%
    ggplot(aes(y = sync_value, x = Partner, color = choice))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.3),
               fun.args = list(mult = 1))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.3))+
  theme_bw()+
  labs(title = "Sync value for each agent by participant choice w/o 11/12")

dat_clean2 %>% 
  filter(!participant %in% c("11_12")) %>%
  ggplot(aes(y = sync_value, x = Partner))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.3),
               fun.args = list(mult = 1))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.3))+
  theme_bw()+
  labs(title = "Sync valye for each actual partner w/o 11/12")

dat_clean2 %>% 
  filter(!participant %in% c("11_12")) %>%
  ggplot(aes(y = sync_value, x = Partner, color = choice))+
  geom_point(shape = 1, alpha = .8, position = position_jitterdodge(.1))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.8),
               fun.args = list(mult = 1.96))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.8))+
  theme_bw()+
  labs(title = "Sync valye for each agent by participant choice with individual data points w/o 11/12")

  
```

## Percentage of "cheating"
```{r}
library(knitr)
kable(dat_clean %>%
  group_by(participant) %>%
  summarize(n_cheat = 200-length(key_respLeft.rt),
            cheat_percent = n_cheat/200*100))

kable(dat_clean %>%
  group_by(participant, Block.thisN) %>%
  summarize(n_cheat = 10-length(key_respLeft.rt),
            cheat_percent = n_cheat/10*100))

```
## Remove participants 11/12 and 10/11

```{r}
dat_clean2 %>% 
  filter(!participant %in% c("11_12", "9_10")) %>%
    ggplot(aes(y = sync_value, x = Partner, color = choice))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.3),
               fun.args = list(mult = 1))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.3))+
  theme_bw()+
  labs(title = "Sync value for each agent by participant choice")

dat_clean2 %>% 
  filter(!participant %in% c("11_12", "9_10")) %>%
  ggplot(aes(y = sync_value, x = Partner))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.3),
               fun.args = list(mult = 1))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.3))+
  theme_bw()+
  labs(title = "Sync valye for each actual partner")

dat_clean2 %>% 
  filter(!participant %in% c("11_12", "9_10")) %>%
  ggplot(aes(y = sync_value, x = Partner, color = choice))+
  geom_point(shape = 1, alpha = .8, position = position_jitterdodge(.1))+
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               width = .1, position = position_dodge(.8),
               fun.args = list(mult = 1.96))+
  stat_summary(fun.data = mean_se, geom = "point", size = 5, 
               position = position_dodge(.8))+
  theme_bw()+
  labs(title = "Sync valye for each agent by participant choice with individual data points")


```

